---
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{flushleft}}
  - \posttitle{\end{flushleft}}
---

```{r setup, include=FALSE,warning=FALSE,  message=FALSE}
library(ragg)
knitr::opts_chunk$set(echo = TRUE,dev = "ragg_png", cache=TRUE) 
WRITE_PLOTS<<-TRUE
```



```{r includes,warning=FALSE,  message=FALSE}
library(here)
code<-here("R_script")
data<-here("Data")
figure_parts<-here("figure_parts")
source(here(code,"paper_common.R"))
source(here(code,"plot_common.R"))
emm_sig_summary_paper<-emm_sig_summary_paper

```


```{r paper_heading,warning=FALSE,  message=FALSE, echo=FALSE}

a<-("From:\n")
b<-(read_file(here("title.txt")))
c<-(read_file(here("authors.txt")))

title<-paste("Analysis underlying figure 5 from ",b)
authors<-paste("By: ",c)

```

## determine which animals demonstrated rapid recovery of AKI by creatinine

For this calculation, the baseline creatinine is the "hospital admission relevant" time zero value, not the pre-injury value.

```{r time to creat recovery, warning=FALSE, message=FALSE}

cr<-M%>%select(x,plCR,x_units, plCK,plCR_units,weight_kg,animal,last_hr)%>%
  mutate(cr=plCR,y=plCR, units_x=x_units, plCK=plCK,units_y=plCR_units,weight=weight_kg)
cr<-cr%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))

thresh=1.5
max_thresh=0.7


last_cr<-cr%>%group_by(animal)%>%mutate(plCRisna=is.na(plCR))%>%select(animal,x,plCR,plCRisna)

cr<-cr%>%group_by(animal)%>%
  mutate(base_cr=plCR[x==0])%>% #baseline here is "hospital admission" not actual baseline
  mutate(cr2h=plCR[x==2])%>%
  mutate(CK_base=plCK[x==-1])%>%
  mutate(CK2h=plCK[x==2])%>%
  mutate(CKdelta2h=CK2h-CK_base)%>%
  mutate(cr48=plCR[x==max(x)])%>%
  mutate(frac_cr48_base=cr48/base_cr)%>%
  mutate(maxCR=max(plCR,na.rm=T))%>%
  mutate(cr48_lte_thresh_x_base=cr48<=thresh*base_cr)%>%
  mutate(cr48_lte_thresh_x_max=cr48<=max_thresh*maxCR)%>%
  mutate(frac_cr48_max=cr48/maxCR)%>%
  mutate(mult_max_base=maxCR/base_cr)%>%
  mutate(maxCK=max(plCK,na.rm=T))%>%
  ungroup()

rrcr<-cr%>%group_by(animal)%>%reframe(animal,tx,base_cr,cr48,maxCR,frac_cr48_base,frac_cr48_max,cr48_lte_thresh_x_base,cr48_lte_thresh_x_max)%>%distinct


rrcr<-rrcr%>%mutate(tx=fct_relevel(tx,"veh", "cil"))
rrcr<-rrcr%>%mutate(tx=relevel(tx,ref="veh"))
rrcr<-droplevels(rrcr)
pcr<-table(rrcr$tx,rrcr$cr48_lte_thresh_x_max)

chisq.test(pcr,simulate.p.value = T,B=10000)
rownames(pcr)<-c("veh","cil")
colnames(pcr)<-c("Nonrecovery","Recovery")
pcr 

```



# Data from the potential study population

3 papers from KwaZulu-Natal and Cape Town describe a population of blunt trauma patients with crush syndrome. 2 additional papers from China describe crush syndrome in earthquake victims.

## South Africa, blunt trauma.

(<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1279914/>) A description of AKI after "punishment beatings". (<https://pubmed.ncbi.nlm.nih.gov/33944766/>) mean CK 5311, at this CK mean cr 1.6 (mg/dL) at admission, South Africa (SA), blunt trauma--essentially the currently proposed population for this study. IQR=44, which is sCr 0.5 mg/dL, which is sd=0.4. (<https://pubmed.ncbi.nlm.nih.gov/30463744/>) (mean cr on presentation to SA trauma service with AKI 2.2), all comers.

## Earthquakes.

(<https://pubmed.ncbi.nlm.nih.gov/32008829>) (mean cr 1.9 +- 0.65), earthquake crush syndrome pts with AKI. (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2865457/>) mean cr 1.85 (163), earthquake crush syndrome pts.

Taken together, these papers suggest that the South African population may be representative of a reified/aggregate human population with crush syndrome. In the South African population with access to medical care, baseline creatinine is 1.6 +/- 0.4 mg/dL. We will take this as the powering baseline.


We have followed the powering method of simulation, using these two resources:

(<https://nickch-k.github.io/EconometricsSlides/Week_08/Power_Simulations.html>) (<https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-11-94>)



```{r modeling pig creatinine, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}


SAmean<-1.6
SAsd<-0.4

cr<-cr%>%mutate(tx=fct_relevel(tx,"veh", "cil"))
cr<-cr%>%mutate(tx=relevel(tx,ref="veh"))
cr<-droplevels(cr)

cr<-cr%>%group_by(animal)%>%mutate(cr.delta=max(plCR,na.rm=T)-plCR[x==0])

PmultCRm<-cr%>%group_by(animal)%>%select(mult_max_base)%>%distinct()%>%ungroup()%>%summarize(mean=mean(mult_max_base, na.rm=T))%>%unlist()

PmultCRsd<-cr%>%group_by(animal)%>%select(mult_max_base)%>%distinct()%>%ungroup()%>%summarize(sd=sd(mult_max_base, na.rm=T))%>%unlist()

smallcr<-cr%>%group_by(animal)%>%select(animal,CKdelta2h, CK2h,base_cr,maxCK,maxCR,cr48,tx,weight_kg)%>%distinct()

model_base_max<-lm(maxCR~base_cr, data=filter(smallcr,tx!="cil"))
summary(model_base_max)

model_max_48<-lm(cr48~maxCR+tx, data=smallcr)
summary(model_max_48)

get_kdigo_stage<-function (baseline, later){ #modified from the epocakir package
  dplyr::case_when(later >= 4 ~ 3,
                   later >= 3 * baseline ~ 3,
                   later >= 2 * baseline ~ 2,
                   later >= 1.5 * baseline ~ 1,
                   later >= (baseline+0.3) ~ 1,
                   TRUE ~ NA)
}

determine_power<-function(iterations=10, startn=200, stopn=200, alpha=0.05,statmodel_base_max,statmodel_48, max_thresh=0.7) {
  t_df<-data.frame()
  for (n in startn:stopn){
    if (n%%10==0){print(n)}
    chi.rec7.at.48<-c()
    p.recovered.at.48<-c()

        for (i in 1:iterations){
      assignment.cila<-sample(c("cil","veh"), n, replace = TRUE, prob = c(0.5,0.5)) 
      sim.sa.admit.cr<-rnorm(n,SAmean,SAsd)
      popdf<-data.frame(tx=assignment.cila,base_cr=sim.sa.admit.cr)
      popdf$x<-48
      popdf$maxCR<-predict(statmodel_base_max,newdata=popdf)
      popdf$cr48<-predict(statmodel_48,newdata=popdf)
      popdf<-popdf%>%mutate(pred.max48delta=maxCR-cr48)
      popdf<-popdf%>%mutate(cr48_lte_thresh_x_max=(cr48<=max_thresh*maxCR))

      chi.table<-table(popdf$tx,popdf$cr48_lte_thresh_x_max)

      test<-chisq.test(chi.table,correct=FALSE)

      p.recovered.at.48[i]<-test$p.value[[1]]

      
    }
    n_df<-data.frame(p.recovered.at.48,n=n,alpha=alpha)
    t_df<-bind_rows(t_df,n_df)
  }
  
  
  return (t_df)
}
```

Now we call the function.

```{r doing the power simulation, eval=TRUE,echo=TRUE, warning=FALSE, error=FALSE, message=FALSE}
iterations=500

power_curve<-determine_power(startn=20, stopn=200, iterations=iterations,alpha=0.01,model_base_max,model_max_48,max_thresh=0.7)


z<-power_curve%>%group_by(n)%>%summarise(p.recovered.at.48=p.recovered.at.48,alpha=alpha,n=n,                                         power.p.recovered.at.48=sum(ifelse(p.recovered.at.48<alpha,TRUE,FALSE))/n(),
                                         )%>%ungroup()

```

Once we've done the power calculation, we can plot the data and use it to make some decisions.

Each dot is the result of a simulated complete study.

```{r eval results, eval=FALSE,echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
#powerdata<-read_csv("power_data_07292023.csv")
powerdata<-z
```

```{r plot code, eval=TRUE,echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

ylab<-"p value"
title<-"p_val_recovery.tiff"     
pvalplot<-ggplot(power_curve, aes(x=n,y=p.recovered.at.48))+
  geom_point(size=0.01,alpha=0.2)+
  geom_smooth()+
  geom_hline(yintercept=0.05, linetype = "dashed", alpha=0.3, color="red")+
  geom_hline(yintercept=0.01, linetype = "dashed", alpha=0.3, color="red")+
  coord_cartesian(ylim=c(0,0.25))+
  theme_classic()+
   ylab(ylab)+
  ggtitle("Creatinine recovery at 48h")

pvalplot
if(WRITE_PLOTS){ggsave(filename=here(figure_parts,title),plot=pvalplot, width=3.0, height=2.25,dpi=300,units="in")}


ylab<-"Power"
title<-"power_recovery.tiff" 
powerplot<-ggplot(z,aes(x=n,y=power.p.recovered.at.48))+
  geom_point(size=0.01,alpha=0.1)+
  geom_hline(yintercept=0.8, linetype = "dashed", alpha=0.3, color="red")+
  geom_hline(yintercept=0.9, linetype = "dashed", alpha=0.3, color="red")+
  geom_smooth()+
  theme_classic()+
  ylab(ylab)+
  ggtitle("Creatinine recovery at 48h")

powerplot
if(WRITE_PLOTS){ggsave(filename=here(figure_parts,title),plot=powerplot, width=3.0, height=2.25,dpi=300,units="in")}

```

It is computationally convenient to extract the n from the power plots.

```{r plot to extract the model data, eval=TRUE,echo=TRUE, warning=TRUE, error=TRUE, message=TRUE}

power_data<-ggplot_build(powerplot) 
q<-power_data$dat[[1]]
n90<-min(q$x[q$y>0.9]) 
n80<-min(q$x[q$y>0.8]) 
print(n80)

```



## Power estimates

After performing Monte Carlo simulation of `r iterations` clinical trials we have the following result:

At alpha=0.01, 80% power for the outcome of creatinine recovery to 70% of maximal at 48h after injury is provided by `r toString(n80)` total patients.

At alpha=0.01, 90% power for the outcome of creatinine recovery to 70% of maximal at 48h after injury is provided by `r n90` total patients.
