---
title: "Cila-Calcil: Testing for difference/nondifference"
author: "Michael Hutchens"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: "word-styles-reference-01.docx"
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("paper_common.R")
source("plot_common.R")
detach('package:lmerTest')
table_column_names<-c("Contrast","Time(h)"," Estimate","SE ","df ","t.ratio","p.value")
```

## Did adding calcitriol to cilastatin sodium have any effect on renal or other physiology?

The study was planned to test vehicle versus cilastatin sodium, and to secondarily test whether a putative loss of vitamin D in the urine due to megalin inhibition by cilastatin caused any harm which could be ameliorated by calcitriol administration. However, surveillance of plasma vitamin D level did not reveal significant drug-mediated change after injury or calcitriol administration. Plasma calcium was unchanged by calcitriol administration. When we investigated plasma calcitriol, although calcitriol in plasma rose in some animals, there was not a significant difference induced by administration of calcitriol, likely because of heterogeneity in baseline plasma calcitriol and perhaps because injury itself caused increased plasma calcitriol. This prompted the hypothesis that calcitriol+cilastatin sodium was nondifferent than cilastatin sodium alone.

In the analysis that follows, tables presenting p values present values derived from post-hoc pairwise comparison with Sidak's correction.

## Calcitriol and injury as measured by plasma creatine kinase

Administration of calcitriol did not significantly alter plasma creatine kinase.

```{r plasma creatine kinase, echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma creatine kinase --------------------------
ylab<-"Plasma Creatine Kinase (IU/L)"
title<-"plCK_calcil_cila.tiff"
star_y<-1.4
plCK<-M%>%select(x,plCK,x_units,weight_kg,animal)%>%
  mutate(plCK=plCK,y=plCK, units_x=x_units, weight=weight_kg)
plCK<-plCK%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plCK)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
##emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plCK,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```

## Calcitriol and plasma calcium

Administration of calcitriol also did not significantly alter plasma calcium.

```{r plasma calcium, echo=FALSE,message=FALSE, results="show", warning=FALSE}

# ionized calcium --------------------------
ylab<-"Plasma Ionized Calcium (mmol/L)"
title<-"pliCa_calcil_cila.tiff"
star_y<-1.4
pliCa<-M%>%select(x,pliCa,x_units,weight_kg,animal)%>%
  mutate(pliCa=pliCa,y=pliCa, units_x=x_units, weight=weight_kg)
pliCa<-pliCa%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=pliCa)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(pliCa,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)

p<-p+ylim(0,2.2)

#write the plot
print(p)

```

## Effect of administered calcitriol on plasma calcitriol

Next we tested (in a subset of animals) whether plasma calcitriol was increased by administered calcitriol. There was wide variation, but no statistically significant effect of calcitriol administration on calcitriol plasma level.

```{r vitamin D assay, echo=FALSE,message=FALSE, results="show", warning=FALSE}
title<-"plasma Calcitriol_calcil_vs_cila.tiff"
ylab<-"Plasma Calcitriol (pg/mL)"

plCal<-M%>%select(x,plCal,plCal_units,weight_kg,animal)%>%
  mutate(y=plCal, units_y=plCal_units, weight=weight_kg)
plCal<-plCal%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))



model<-lmer(y~tx*as.factor(x)+(1|animal),data=plCal)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)

p<-column_scatter_errorbar_plot(plCal,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                xlabel="Time (h)",ylabel=ylab)

thisplot_left_legend<-c(0.13,0.95)
p<-p+theme(legend.position = left_legend)
print(p)
          

```

## Calcitriol-induced nonrenal physiologic effect or noneffect

Next we investigated effects of calcitriol+cilastatin versus cilastatin alone on heart rate, mean arterial pressure, urine output, and temperature.

```{r cila-calcil effect on physiology HR, echo=FALSE,message=FALSE, results="show", warning=FALSE}
#HR, MAP, Temp, UOP
title<-"HR_calcil_vs_cila.tiff"
ylab<-"Heart rate (bpm)"

HR<-M%>%select(x,hr, hr_rollm,map_quality,x_units,hr_units,weight_kg,animal)%>%
  mutate(HR=hr_rollm,y=HR, units_x=x_units, units_y=hr_units,weight=weight_kg)
HR<-HR%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

xlab<-"Time (h)"
maxy<-setmaxY(max(HR$y))
pY=maxy/20*19

p<-ggplot(HR,aes(x=x,y=y,fill=tx,color=tx))+
  scale_color_manual(values=redblue, aesthetics=c("color", "fill"))+
  geom_boxplot(outlier.size = 0.5,aes(x=factor(x),fill=tx)) +
  scale_x_discrete(breaks=timepoints) +
  labs(x=xlab, y=ylab,tx="Treatment") +
  plot_theme_wide+
  ylim(0,maxy)
thisplot_left_legend<-c(0.3,0.95)
#p<-p+theme(legend.position = thisplot_left_legend)
#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=HR)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#add stars to plot
p<-p+annotate("text", x=pair_summary$x+1,y=pY,label=pair_summary$star, size=6)

print(p)


```

6h after drug administration, heart rate was transiently lower in calcitriol-treated animals. The significance of this difference is supported by the trend in the prior 5 hours. The difference in means is about 11 beats per minute, which could have physiologic significance, it is about 10% of the mean heart rate.

```{r cila-calcil effect on physiology MAP, echo=FALSE,message=FALSE, results="show", warning=FALSE}
#HR, MAP, Temp, UOP
title<-"MAP_calcil_vs_cila.tiff"
ylab<-"Mean arterial pressure (mmHg)"

MAP<-M%>%select(x,map_rollm,map_quality,x_units,map_units,weight_kg,animal,map_rollm)%>%
  mutate(MAP=map_rollm,y=MAP,quality=map_quality, units_x=x_units, units_y=map_units,weight=weight_kg)
MAP<-MAP%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

xlab<-"Time (h)"
p<-ggplot(MAP,aes(x=x,y=y,fill=tx,color=tx))+
  scale_color_manual(values=redblue, aesthetics=c("color", "fill"))+
  geom_boxplot(outlier.size = 0.5,aes(x=factor(x),fill=tx)) +
  scale_x_discrete(breaks=timepoints) +
  labs(x=xlab, y=ylab,tx="Treatment") +
  plot_theme_wide+
  ylim(0,100)
thisplot_left_legend<-c(0.3,0.95)
p<-p+theme(legend.position = thisplot_left_legend)
#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=MAP)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#add stars to plot
p<-p+annotate("text", x=pair_summary$x+1,y=90,label=pair_summary$star, size=6)

p


```

Calcitriol did not alter blood pressure.

```{r cila-calcil effect on physiology UOP, echo=FALSE,message=FALSE, results="show", warning=FALSE}

title<-"UOP_calcil_vs_cila.tiff"
ylab<-"UOP (mL/kg)"

UOP<-M%>%select(x,uop_rate,uop_quality,x_units,uop_units,weight_kg,animal)%>%
  mutate(UOP=uop_rate,y=UOP/weight_kg, units_x=x_units, units_y=uop_units,weight=weight_kg)
UOP<-UOP%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=1)&(x<=48))

#plot

xlab<-"Time (h)"
maxy<-setmaxY(max(UOP$y))
maxy<-0.5
pY=maxy/20*17

p<-ggplot(UOP,aes(x=x,y=y,fill=tx,color=tx))+
  scale_color_manual(values=redblue, aesthetics=c("color", "fill"))+
  geom_boxplot(outlier.size = 0.5,aes(x=factor(x),fill=tx)) +
  scale_x_discrete(breaks=timepoints) +
  labs(x=xlab, y=ylab,tx="Treatment") +
  plot_theme_wide+
  ylim(0,maxy)
thisplot_left_legend<-c(0.3,0.95)
#p<-p+theme(legend.position = thisplot_left_legend)
#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=UOP)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#add stars to plot
p<-p+annotate("text", x=pair_summary$x+1,y=pY,label=pair_summary$star, size=6)


print(p)


```

Urine output was statistically different at 1, 41, and 42h. The mean difference in urine output at 1h was 0.02 mL/kg, or about 1 mL for the hour. This is a clinically/physiologically nonrelevant difference. At 41 and 42 hours, the difference was 0.01 mL/kg.

```{r cila-calcil effect on physiology Temperature, echo=FALSE,message=FALSE, results="show", warning=FALSE}
#HR, MAP, Temp, UOP
title<-"TEMP_calcil_vs_cila.tiff"
ylab<-"Temperature (C)"

TEMP<-M%>%select(x,temp_rollm,temp_quality,x_units,temp_units,weight_kg,animal)%>%
  mutate(TEMP=temp_rollm,y=TEMP, units_x=x_units, units_y=temp_units,weight=weight_kg)
TEMP<-TEMP%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=1)&(x<=48))

#plot

xlab<-"Time (h)"
maxy<-setmaxY(max(TEMP$y))
pY=maxy/20*19

p<-ggplot(TEMP,aes(x=x,y=y,fill=tx,color=tx))+
  scale_color_manual(values=redblue, aesthetics=c("color", "fill"))+
  geom_boxplot(outlier.size = 0.5,aes(x=factor(x),fill=tx)) +
  scale_x_discrete(breaks=timepoints) +
  labs(x=xlab, y=ylab,tx="Treatment") +
  plot_theme_wide+
  ylim(30,maxy)
thisplot_left_legend<-c(0.3,0.95)
#p<-p+theme(legend.position = thisplot_left_legend)
#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=TEMP)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#add stars to plot
p<-p+annotate("text", x=pair_summary$x+1,y=pY,label=pair_summary$star, size=6)

print(p)


```

Temperature was not influenced by calcitriol administration.

## Calcitriol effect on renal function: serum creatinine

Calcitriol had no effect on creatinine.

```{r plasma creatinine ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma creatinine --------------------------
ylab<-"Serum Creatinine (mmol/L)"
title<-"plCR_calcil_cila_alone.tiff"
plCR<-M%>%select(x,plCR,x_units,weight_kg,animal)%>%
  mutate(y=plCR, units_x=x_units, weight=weight_kg)
plCR<-plCR%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plCR)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plCR,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)

p<-p+ylim(0,2.2)
thisplot_left_legend<-c(0.13,0.95)
p<-p+theme(legend.position = left_legend)
#write the plot
print(p)

```

## Calcitriol effect on renal function: blood urea nitrogen

Calcitriol did not affect blood urea nitrogen; interestingly the trend, if any, is opposite that of serum creatinine.

```{r plasma blood urea nitrogen ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma urea nitrogen --------------------------
ylab<-"Blood urea Nitrogen (mmol/L)"
title<-"plBUN_calcil_cila_alone.tiff"
plBUN<-M%>%select(x,plBUN,x_units,weight_kg,animal)%>%
  mutate(y=plBUN, units_x=x_units, weight=weight_kg)
plBUN<-plBUN%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plBUN)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plBUN,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```

## Calcitriol effect on renal function: potassium

Calcitriol administration did not affect plasma potassium.

```{r plasma potassium ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma potassium --------------------------
ylab<-"Plasma potassium (mmol/L)"
title<-"plK_calcil_cila_alone.tiff"
plK<-M%>%select(x,plK,x_units,weight_kg,animal)%>%
  mutate(y=plK, units_x=x_units, weight=weight_kg)
plK<-plK%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plK)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plK,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```

## Calcitriol effect on renal function: GFR

Lastly, administered calcitriol had no effect on 6, 24, or 48h GFR.

```{r  GFR ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma potassium --------------------------
ylab<-"GFR"
title<-"GFR_calcil_cila_alone.tiff"
GFR<-M%>%select(x,gfr,x_units,weight_kg,animal)%>%
  mutate(y=gfr, units_x=x_units, weight=weight_kg)
GFR<-GFR%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=GFR)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
knitr::kable((summary(pairs_model)), format = "pipe", padding = 0,digits=3, col.names=table_column_names)
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(GFR,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```
