---
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{flushleft}}
  - \posttitle{\end{flushleft}}
---


```{r setup, include=FALSE,warning=FALSE,  message=FALSE}
library(ragg)
knitr::opts_chunk$set(echo = TRUE,dev = "ragg_png", cache=TRUE) 
WRITE_PLOTS<<-TRUE
```

```{r includes,warning=FALSE,  message=FALSE}
library(here)
code<-here("R_script")
data<-here("Data")
figure_parts<-here("figure_parts")
source(here(code,"paper_common.R"))
source(here(code,"plot_common.R"))
emm_sig_summary_paper<-emm_sig_summary_paper

```

```{r paper_heading,warning=FALSE,  message=FALSE, echo=FALSE}

a<-("From:\n")
b<-(read_file(here("title.txt")))
c<-(read_file(here("authors.txt")))

title<-paste("Analysis underlying figure 6 from ",b)
authors<-paste("By: ",c)

```


## Creatine Kinase (CK)

```{r CK,warning=FALSE,  message=FALSE}
ylab<-"Plasma CK (IU/L)*1000"
title<-"CK_cil_veh.tiff"

ck<-M%>%select(x,plCK,x_units,plCK_units,weight_kg,animal)%>%
  mutate(ck=plCK,y=plCK/1000, units_x=x_units, units_y=plCK_units,weight=weight_kg)
ck<-ck%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=ck)
summary(model)       
model2<-lmer(y~tx*x+(1|animal),data=ck)
summary(model2)
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(ck$y))
brackets_table<-pairs_to_significance_table(pair_summary,maxy)


p<-column_scatter_errorbar_plot(ck,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=FALSE,
                                xlabel="Time (h)",ylabel=ylab)
thisplot_left_legend<-c(0.35,0.95)
p<-p+theme(legend.position = thisplot_left_legend)
p
#write the plot

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

#summary statistics for significant values formatted to place in the text of the paper
emm_sig_summary_paper(ck,pair_summary,emm_means)

```


## Plasma myoglobin (plMB)

```{r MB,warning=FALSE,  message=FALSE}
ylab<-"Plasma Mb (ng/mL)"
title<-"plMb_cil_veh.tiff"

mb<-M%>%select(x,plMB,x_units,,weight_kg,animal)%>%
  mutate(y=plMB, units_x=x_units,weight=weight_kg)
mb<-mb%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=mb)
summary(model)       

resid_panel(model)
meets_assumptions=FALSE 

if(meets_assumptions==FALSE){
  #non-normal, therefore use rmodel for outlier-robust lmer
    model<-rlmer(y~tx*as.factor(x)+(1|animal),data=mb)
    model_time_nofactor<-lmerTest::lmer(y~tx*x+(1|animal),data=mb)
}

summary(model)
summary(model_time_nofactor)
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(mb$y))
brackets_table<-pairs_to_significance_table(pair_summary,maxy)


p<-column_scatter_errorbar_plot(mb,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=TRUE,p_bracketsdata=brackets_table,bracket_nudge=-10000,
                                xlabel="Time (h)",ylabel=ylab)
thisplot_left_legend<-c(0.35,0.95)
p<-p+theme(legend.position = thisplot_left_legend)
p
#write the plot

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

#summary statistics for significant values formatted to place in the text of the paper
emm_sig_summary_paper(mb,pair_summary,emm_means)

```

## Urine myoglobin (urMB)/Plasma myoglobin (plMB)

```{r upMB,warning=FALSE,  message=FALSE}
ylab<-"Urine/Plasma Mb"
title<-"urplMb_cil_veh.tiff"

mb<-M%>%select(x,urMB,plMB,x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=(urMB*uop_rate)/plMB, units_x=x_units,weight=weight_kg)
mb<-mb%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=2)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=mb)
summary(model)       
model2<-lmer(y~tx*x+(1|animal),data=mb)
summary(model2)
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(mb$y))
brackets_table<-pairs_to_significance_table(pair_summary,maxy)


p<-column_scatter_errorbar_plot(mb,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=TRUE,p_bracketsdata=brackets_table,bracket_nudge=-0.95,
                                xlabel="Time (h)",ylabel=ylab)
#thisplot_left_legend<-c(0.35,0.95)
#p<-p+theme(legend.position = thisplot_left_legend)
p
#write the plot

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

#summary statistics for significant values formatted to place in the text of the paper
emm_sig_summary_paper(mb,pair_summary,emm_means)

```


## Urine porphyrin (urPOR) mass alone

```{r upPORalone,warning=FALSE,  message=FALSE}
ylab<-"Urine Por (mg)"
title<-"urPOR_cil_veh.tiff"

por<-M%>%select(x,urPOR,plMB,x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=urPOR*uop_rate, units_x=x_units,weight=weight_kg)
por<-por%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=2)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=por)
summary(model)       
model2<-lmer(y~tx*x+(1|animal),data=por)
summary(model2)
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(por$y))
brackets_table<-pairs_to_significance_table(pair_summary,maxy)


p<-column_scatter_errorbar_plot(por,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=TRUE,p_bracketsdata=brackets_table,bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)
#thisplot_left_legend<-c(0.35,0.95)
#p<-p+theme(legend.position = thisplot_left_legend)
p
#write the plot

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

#summary statistics for significant values formatted to place in the text of the paper
emm_sig_summary_paper(por,pair_summary,emm_means)




```
## Urine porphyrin (urPOR)/Plasma porphyrin (plPOR)

```{r upPOR,warning=FALSE,  message=FALSE}
ylab<-"Urine Por/Plasma Mb"
title<-"urplPOR_cil_veh.tiff"

por<-M%>%select(x,urPOR,plMB,x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=(urPOR*uop_rate)/plMB, units_x=x_units,weight=weight_kg)
por<-por%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=2)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=por)
summary(model)       
model2<-lmer(y~tx*x+(1|animal),data=por)
summary(model2)
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(por$y))
brackets_table<-pairs_to_significance_table(pair_summary,maxy)


p<-column_scatter_errorbar_plot(por,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=TRUE,p_bracketsdata=brackets_table,bracket_nudge=-1.0998,
                                xlabel="Time (h)",ylabel=ylab)
#thisplot_left_legend<-c(0.35,0.95)
#p<-p+theme(legend.position = thisplot_left_legend)
p
#write the plot

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

#summary statistics for significant values formatted to place in the text of the paper
emm_sig_summary_paper(por,pair_summary,emm_means)




```

## Total urinary porphyrin excretion

```{r porphyrin auc}
ylab<-"48h Porphyrin Excretion (AUC)"
title<-"urpor_AUC_cil_veh.tiff"  
por<-M%>%select(x,urPOR,plMB,x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=(urPOR*uop_rate)/plMB, units_x=x_units,weight=weight_kg)
por<-por%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=2)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))
por_aucs<-por%>%group_by(animal)%>%mutate(PorExc=urPOR*uop_rate/plMB)%>%ungroup()
por_aucs<-calc_auc(por_aucs, target="PorExc")%>%select(animal,tx, PorExc_auc)%>%filter(!is.na(PorExc_auc))%>%distinct()
por_aucs<-por_aucs%>%mutate(tx=fct_relevel(tx, "cil",after=Inf))
            
por_t<-t.test(PorExc_auc~tx,data=por_aucs)   
por_aucs%>%group_by(tx)%>%summarize(mean_auc=mean(PorExc_auc), sd_auc=sd(PorExc_auc))

#percent reduction
por_aucs<-por_aucs%>%mutate(por_aucs_mean_veh=mean(PorExc_auc[tx=="veh"]))
por_aucs<-por_aucs%>%rowwise()%>%mutate(pct_inc_por_auc=(PorExc_auc-por_aucs_mean_veh)/por_aucs_mean_veh*100)

por_aucs%>%group_by(tx)%>%summarize(mincrease=mean(pct_inc_por_auc), sd=sd(pct_inc_por_auc))



p<-column_scatter_errorbar_plot(por_aucs,x=tx,y=PorExc_auc, groupvar=tx,themevar=plot_theme_squareish2,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=FALSE,
                                xlabel="Treatment",ylabel=ylab)
p<-p+geom_signif(xmin=1,
                                    xmax=2,
                                   y_position=0.0025,
                                   annotation=paste0("p= ",as.character(round(por_t$p.value,3))),
                                   tip_length = 0.025,
                                    color="black",
                                    vjust=-1)

p

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

por_t
```

## Total urinary porphyrin excretion indexed to creatinine (reviewer 3)

```{r porphyrin-cr auc}
ylab<-"48h Urine Porphyrin (\u00B5g/\u00B5g Cr*48h)"
ylab
title<-"urporCR_AUC_cil_veh.tiff" 
#coefficients in mutate  below to deal with units
por<-M%>%select(x,urPOR,plMB,urCR,x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=(((urPOR)/(urCR/10))*uop_rate)/(plMB/1e6), units_x=x_units,weight=weight_kg)
por<-por%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  #group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  #filter(x%%1==0)%>%
  filter((x>=0)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

por_aucs<-por%>%group_by(animal)%>%mutate(PorExc=y)%>%ungroup()
por_aucs<-calc_auc(por_aucs, target="PorExc")%>%select(animal,tx, PorExc_auc)%>%filter(!is.na(PorExc_auc))%>%distinct()
por_aucs<-por_aucs%>%mutate(tx=fct_relevel(tx, "cil",after=Inf))
            
por_t<-t.test(PorExc_auc~tx,data=por_aucs)   
por_aucs%>%group_by(tx)%>%summarize(mean_auc=mean(PorExc_auc), sd_auc=sd(PorExc_auc))

#percent reduction
por_aucs<-por_aucs%>%mutate(por_aucs_mean_veh=mean(PorExc_auc[tx=="veh"]))
por_aucs<-por_aucs%>%rowwise()%>%mutate(pct_inc_por_auc=(PorExc_auc-por_aucs_mean_veh)/por_aucs_mean_veh*100)

por_aucs%>%group_by(tx)%>%summarize(mincrease=mean(pct_inc_por_auc), sd=sd(pct_inc_por_auc))



p<-column_scatter_errorbar_plot(por_aucs,x=tx,y=PorExc_auc, groupvar=tx,themevar=plot_theme_squareish2,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=FALSE,
                                xlabel="Treatment",ylabel=ylab)
p<-p+geom_signif(xmin=1,
                                    xmax=2,
                                   y_position=300,
                                   annotation=paste0("p= ",as.character(round(por_t$p.value,3))),
                                   tip_length = 0.025,
                                    color="black",
                                    vjust=-1)

p

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

por_t
```



## Total urinary myoglobin excretion

```{r myoglobin auc}
ylab<-"48h Urine Mb (mg/mg Cr*48h)"
title<-"urmb_AUC_cil_veh.tiff"  


por<-M%>%select(x,urMB,plMB,urCR,x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=(((urMB/1e6)/(urCR))*uop_rate)/(plMB/1e6), units_x=x_units,weight=weight_kg)
por<-por%>%
  filter(x%in%sched_urine_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=2)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))
por_aucs<-por%>%group_by(animal)%>%mutate(MBExc=y)%>%ungroup()
por_aucs<-calc_auc(por_aucs, target="MBExc")%>%select(animal,tx, MBExc_auc)%>%filter(!is.na(MBExc_auc))%>%distinct()
por_aucs<-por_aucs%>%mutate(tx=fct_relevel(tx, "cil",after=Inf))
            
por_t<-t.test(MBExc_auc~tx,data=por_aucs)   


p<-column_scatter_errorbar_plot(por_aucs,x=tx,y=MBExc_auc, groupvar=tx,themevar=plot_theme_squareish2,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=FALSE,
                                xlabel="Treatment",ylabel=ylab)
p<-p+geom_signif(xmin=1,
                                    xmax=2,
                                   y_position=0.0075,
                                   annotation=paste0("p= ",as.character(round(por_t$p.value,3))),
                                   tip_length = 0.025,
                                    color="black",
                                    vjust=-1)

p

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

```

## Urine protein (Reviewer 1 requested this analysis)

```{r uBCA,warning=FALSE,  message=FALSE}
ylab<-"Urine Protein (ug/mg Cr)"
title<-"urBCA_cil_veh.tiff"

bca<-M%>%select(x,urBCA,plBCA,urCR,x_units,uop_rate,weight_kg,animal)%>%
  #mutate(y=(urBCA), units_x=x_units,weight=weight_kg)
  #mutate(y=(urBCA*uop_rate), units_x=x_units,weight=weight_kg)
  mutate(y=(urBCA/urCR)*uop_rate, units_x=x_units,weight=weight_kg)
  #mutate(y=(urBCA*uop_rate)/plBCA, units_x=x_units,weight=weight_kg)
bca<-bca%>%
  filter(x%in%sched_urine_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=bca)
summary(model)   

resid_panel(model)
meets_assumptions=FALSE 

if(meets_assumptions==FALSE){
  #non-normal, therefore use rmodel for outlier-robust lmer
    model<-rlmer(y~tx*as.factor(x)+(1|animal),data=bca)
}

emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(bca$y))
brackets_table<-pairs_to_significance_table(pair_summary,maxy)


p<-column_scatter_errorbar_plot(bca,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=TRUE,p_bracketsdata=brackets_table,bracket_nudge=-0.85,
                                xlabel="Time (h)",ylabel=ylab)

# p<-p+geom_signif(xmin=0.75,
#                                     xmax=1.25,
#                                    y_position=75,
#                                    annotation=paste0("p= ",as.character(round(brackets_table[1,]$p.value,2))),
#                                     textsize=3,
#                                    tip_length = 0.025,
#                                     color="black",
#                                     vjust=-1)
#thisplot_left_legend<-c(0.35,0.95)
#p<-p+theme(legend.position = thisplot_left_legend)
p
#write the plot

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

#summary statistics for significant values formatted to place in the text of the paper
emm_sig_summary_paper(bca,pair_summary,emm_means)

```

## Fractional excretion of myoglobin (reviewer 3 recommended this)

```{r myoglobin fractional excretion}
#Fractional Excretion of Sodium (FENa), % = 100 × (SCr × UMb ) / (SMb × UCr)
#note coefficients below to deal with disparate units.


ylab<-"Fractional excretion of myoglobin"
title<-"FraExc_Mb_cil_veh.tiff"  
femb<-M%>%select(x,urMB,plMB,urCR, plCR, x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=100*((plCR/10)*(urMB/1e6))/((plMB/1e6)*(urCR/10)), units_x=x_units,weight=weight_kg)
femb<-femb%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=2)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=femb)
summary(model)   

resid_panel(model)
meets_assumptions=FALSE 

if(meets_assumptions==FALSE){
  #non-normal, therefore use rmodel for outlier-robust lmer
    model<-rlmer(y~tx*as.factor(x)+(1|animal),data=femb)
}

emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(femb$y))
brackets_table<-pairs_to_significance_table(pair_summary,maxy)




p<-column_scatter_errorbar_plot(femb,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=TRUE,p_bracketsdata=brackets_table,bracket_nudge=-0.2,
                                xlabel="Time (h)",ylabel=ylab)

p

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

```




## Mygoglobin Fractional excretion of porphyrin (reviewer 3 recommended this)

```{r porphyrin fractional excretion}
#Fractional Excretion of Sodium (FENa), % = 100 × (SCr × UMb ) / (SMb × UCr)
#note coefficients below to deal with disparate units.
ylab<-"Mb Fractional excretion of porphyrin"
title<-"FraExc_POR_cil_veh.tiff"  
fepor<-M%>%select(x,urPOR,plMB,urCR, plCR, x_units,uop_rate,weight_kg,animal)%>%
  mutate(y=100*((plCR/10)*(urPOR))/((plMB/1e6)*(urCR/10)), units_x=x_units,weight=weight_kg)
fepor<-fepor%>%
  filter(x%in%sched_urine_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%   
  filter(tx!=shamname)%>%
  filter(x%%1==0)%>%
  filter((x>=2)&(x<=48))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#statistical analysis - lmer followed by adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=fepor)
summary(model)   

resid_panel(model)
meets_assumptions=FALSE 

if(meets_assumptions==FALSE){

    #non-normal, therefore use rmodel for outlier-robust lmer
    model<-rlmer(y~tx*as.factor(x)+(1|animal),data=fepor)
}

emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
spairs
pair_summary<-summary(pairs_model)
pair_summary<-pair_summary%>%mutate(star=pstar_horiz(p.value))


maxy<-setmaxY(max(fepor$y), round=FALSE)
brackets_table<-pairs_to_significance_table(pair_summary,maxy)




p<-column_scatter_errorbar_plot(fepor,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                                scalecolor=scalecolorCV,
                                scalefill=scalefillCV,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,bracket_nudge=-0.00015,
                                xlabel="Time (h)",ylabel=ylab)

p

if(WRITE_PLOTS){ ggsave(filename=here(figure_parts,title),plot=p, width=3.0, height=2.25,dpi=300,units="in")}

```
## Correlation of non-zero urMb and urPOR
```{r porphyrin myoglobin correlation}

ylab<-"urPOR and non-zero urMB"
title<-"urPOR_urMB_scatter.tiff"  
urpormb<-M%>%select(x,urPOR,urMB,urCR, plMB, x_units,uop_rate,weight_kg,animal)
urpormb<-urpormb%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_tx ~ "cil",
    animal%in%sham_sx ~ "no impact",
    animal%in%veh_tx ~ "veh",
  )
  ))%>%
  mutate(tx=fct_relevel(tx, "cil",after=Inf))

#plot
ggplot(urpormb,aes(x=urMB))+
  geom_histogram(bins=100)+
  theme_classic()+
  xlim(0,30)+
  ylim(0,5)

ggplot(urpormb,aes(x=urPOR))+
  geom_histogram(bins=100)+
  theme_classic()+
  xlim(0,0.03)

urpormb<-urpormb%>%filter(urMB>9)

#urpormb<-urpormb%>%filter(x==24)

ggplot(urpormb,aes(x=urMB,y=urPOR,color=tx))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_classic()

ggplot(urpormb,aes(x=plMB,y=urPOR,color=tx))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_classic()

cor.test(urpormb$plMB,urpormb$urPOR)
cor.test(urpormb$urMB,urpormb$urPOR)

model<-lm(urPOR~plMB+tx, data=urpormb)
summary(model)
```
