---
title: "Cila-Calcil: Testing for difference/nondifference"
author: "Michael Hutchens"
date: "`r Sys.Date()`"
output:
  word_document:
    reference_docx: "word-styles-reference-01.docx"
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE,warning=FALSE,  message=FALSE, echo=FALSE}
library(ragg)
knitr::opts_chunk$set(echo = TRUE,dev = "ragg_png", cache=TRUE) 
WRITE_PLOTS<<-FALSE
```

```{r includes,warning=FALSE,  message=FALSE, echo=FALSE}
library(here)
code<-here("R_script")
data<-here("Data")
figure_parts<-here("figure_parts")
source(here(code,"paper_common.R"))
source(here(code,"plot_common.R"))
emm_sig_summary_paper<-emm_sig_summary_paper

```

```{r setup2, echo=FALSE}
detach('package:lmerTest')
table_column_names<-c("Contrast","Time(h)"," Estimate","SE ","df ","t.ratio","p.value")
```

## Did adding calcitriol to cilastatin sodium have any effect on renal or other physiology?

The study was planned to test vehicle versus cilastatin sodium, and to secondarily test whether a putative loss of vitamin D in the urine due to megalin inhibition by cilastatin caused any harm which could be ameliorated by calcitriol administration. In a preplanned analysis, we tested whether renal or other physiology was affected by calcitriol administration. Plasma calcium was unchanged by calcitriol administration, nor were any indices of renal or other physiology. Surveillance of plasma vitamin D level did not reveal significant drug-mediated change after injury or calcitriol administration.

In the analysis that follows, tables presenting p values present values derived from post-hoc pairwise comparison with Sidak's correction.

## Calcitriol and injury as measured by plasma creatine kinase

Administration of calcitriol did not significantly alter plasma creatine kinase.

```{r plasma creatine kinase, echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma creatine kinase --------------------------
ylab<-"Plasma Creatine Kinase (IU/L)"
title<-"plCK_calcil_cila.tiff"
star_y<-1.4
plCK<-M%>%select(x,plCK,x_units,weight_kg,animal)%>%
  mutate(plCK=plCK,y=plCK, units_x=x_units, weight=weight_kg)
plCK<-plCK%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plCK)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
##emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)

pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plCK,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,scalecolor=scalecolorCC,                                 scalefill=scalefillCC,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```

## Calcitriol and plasma calcium

Administration of calcitriol also did not significantly alter plasma calcium.

```{r plasma calcium, echo=FALSE,message=FALSE, results="show", warning=FALSE}

# ionized calcium --------------------------
ylab<-"Plasma Ionized Calcium (mmol/L)"
title<-"pliCa_calcil_cila.tiff"
star_y<-1.4
pliCa<-M%>%select(x,pliCa,x_units,weight_kg,animal)%>%
  mutate(pliCa=pliCa,y=pliCa, units_x=x_units, weight=weight_kg)
pliCa<-pliCa%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=pliCa)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)

pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(pliCa,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,scalecolor=scalecolorCC,                                 scalefill=scalefillCC,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)

p<-p+ylim(0,2.2)

#write the plot
print(p)

```


## Calcitriol-induced nonrenal physiologic effect or noneffect

Next we investigated effects of calcitriol+cilastatin versus cilastatin alone on heart rate, mean arterial pressure, urine output, and temperature.

### Heart Rate

```{r calcitriol_eff_HR, echo=FALSE,include=TRUE,message=FALSE, results="show", warning=FALSE}
#HR, MAP, Temp, UOP echo=FALSE,message=FALSE, results="show", warning=FALSE
title<-"HR_calcil_vs_cila.tiff"
ylab<-"Heart rate (bpm)"

HR<-M%>%select(x,hr, hr_rollm,map_quality,x_units,hr_units,weight_kg,animal)%>%
  mutate(HR=hr_rollm,y=HR, units_x=x_units, units_y=hr_units,weight=weight_kg)
HR<-HR%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))


#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=HR)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)

results_flextable(pair_summary)

pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#plot

p<<-line_scatter_errorbar_plot(HR,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                              scalecolor=scalecolorCC,
                                scalefill=scalefillCC,
                              p_brackets=FALSE,p_bracketsdata=brackets_table,
                               scale_timepoint_breaks = plot_x_timepoints_baseline,
                              xlabel="Time (h)",ylabel=ylab)

stary<-get_star_y(p)

p<<-p+annotate(geom="text", x=pair_summary$x+1,y=stary,label=pair_summary$star,parse=F, 
              family="Lucida Sans Unicode",size=4)


print(p)


```

6h after drug administration, heart rate was transiently lower in calcitriol-treated animals. The significance of this difference is supported by the trend in the prior 5 hours. The difference in means is about 11 beats per minute, which could have physiologic significance, it is about 10% of the mean heart rate.

### Mean Arterial Pressure

```{r calcitriol_eff_MAP, echo=FALSE,message=FALSE, results="show", warning=FALSE}
#HR, MAP, Temp, UOP
title<-"MAP_calcil_vs_cila.tiff"
ylab<-"Mean arterial pressure (mmHg)"

MAP<-M%>%select(x,map_rollm,map_quality,x_units,map_units,weight_kg,animal,map_rollm)%>%
  mutate(MAP=map_rollm,y=MAP,quality=map_quality, units_x=x_units, units_y=map_units,weight=weight_kg)
MAP<-MAP%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))





#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=MAP)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#plot

p<<-line_scatter_errorbar_plot(MAP,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                              scalecolor=scalecolorCC,
                                scalefill=scalefillCC,
                              p_brackets=FALSE,p_bracketsdata=brackets_table,
                               scale_timepoint_breaks = plot_x_timepoints_baseline,
                              xlabel="Time (h)",ylabel=ylab)

stary<-get_star_y(p)

p<<-p+annotate(geom="text", x=pair_summary$x+1,y=stary,label=pair_summary$star,parse=F, 
              family="Lucida Sans Unicode",size=4)

print(p)


```

Calcitriol did not alter blood pressure.

### Urine output

```{r calcitriol_eff_UOP, echo=FALSE,message=FALSE, results="show", warning=FALSE}

title<-"UOP_calcil_vs_cila.tiff"
ylab<-"UOP (mL/kg)"

UOP<-M%>%select(x,uop_rate,uop_quality,x_units,uop_units,weight_kg,animal)%>%
  mutate(UOP=uop_rate,y=UOP/weight_kg, units_x=x_units, units_y=uop_units,weight=weight_kg)
UOP<-UOP%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=1)&(x<=48))



#p<-p+theme(legend.position = thisplot_left_legend)
#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=UOP)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#plot

p<<-line_scatter_errorbar_plot(UOP,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                              scalecolor=scalecolorCC,
                                scalefill=scalefillCC,
                              p_brackets=FALSE,p_bracketsdata=brackets_table,
                               scale_timepoint_breaks = plot_x_timepoints_baseline,
                              xlabel="Time (h)",ylabel=ylab)

stary<-get_star_y(p)
thisplot_left_legend<-c(0.3,0.95)
p<<-p+annotate(geom="text", x=pair_summary$x+1,y=stary,label=pair_summary$star,parse=F, 
              family="Lucida Sans Unicode",size=4)

print(p)



```

Urine output was statistically different at 1, 41, and 42h. The mean difference in urine output at 1h was 0.02 mL/kg, or about 1 mL for the hour. This is a clinically/physiologically nonrelevant difference. At 41 and 42 hours, the difference was 0.01 mL/kg.

### Temperature

```{r calcitriol_eff_Temperature, echo=FALSE,message=FALSE, results="show", warning=FALSE}
#HR, MAP, Temp, UOP
title<-"TEMP_calcil_vs_cila.tiff"
ylab<-"Temperature (C)"

TEMP<-M%>%select(x,temp_rollm,temp_quality,x_units,temp_units,weight_kg,animal)%>%
  mutate(TEMP=temp_rollm,y=TEMP, units_x=x_units, units_y=temp_units,weight=weight_kg)
TEMP<-TEMP%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=1)&(x<=48))


#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=TEMP)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)
pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

#plot

p<<-line_scatter_errorbar_plot(TEMP,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,
                              scalecolor=scalecolorCC,
                                scalefill=scalefillCC,
                              p_brackets=FALSE,p_bracketsdata=brackets_table,
                               scale_timepoint_breaks = plot_x_timepoints_baseline,
                              xlabel="Time (h)",ylabel=ylab)

stary<-get_star_y(p)
thisplot_left_legend<-c(0.3,0.95)
p<<-p+annotate(geom="text", x=pair_summary$x+1,y=stary,label=pair_summary$star,parse=F, 
              family="Lucida Sans Unicode",size=4)

print(p)


```

Temperature was not influenced by calcitriol administration.

### Calcitriol effect on renal function: serum creatinine

Calcitriol had no effect on creatinine.

```{r plasma creatinine ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma creatinine --------------------------
ylab<-"Serum Creatinine (mmol/L)"
title<-"plCR_calcil_cila_alone.tiff"
plCR<-M%>%select(x,plCR,x_units,weight_kg,animal)%>%
  mutate(y=plCR, units_x=x_units, weight=weight_kg)
plCR<-plCR%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plCR)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)

pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plCR,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,scalecolor=scalecolorCC,                                 scalefill=scalefillCC,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)

p<-p+ylim(0,2.2)
thisplot_left_legend<-c(0.13,0.95)
p<-p+theme(legend.position = left_legend)
#write the plot
print(p)

```

## Calcitriol effect on renal function: blood urea nitrogen

Calcitriol did not affect blood urea nitrogen; interestingly the trend, if any, is opposite that of serum creatinine.

```{r plasma blood urea nitrogen ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma urea nitrogen --------------------------
ylab<-"Blood urea Nitrogen (mmol/L)"
title<-"plBUN_calcil_cila_alone.tiff"
plBUN<-M%>%select(x,plBUN,x_units,weight_kg,animal)%>%
  mutate(y=plBUN, units_x=x_units, weight=weight_kg)
plBUN<-plBUN%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plBUN)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plBUN,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,scalecolor=scalecolorCC,                                 scalefill=scalefillCC,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```

## Calcitriol effect on renal function: potassium

Calcitriol administration did not affect plasma potassium.

```{r plasma potassium ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma potassium --------------------------
ylab<-"Plasma potassium (mmol/L)"
title<-"plK_calcil_cila_alone.tiff"
plK<-M%>%select(x,plK,x_units,weight_kg,animal)%>%
  mutate(y=plK, units_x=x_units, weight=weight_kg)
plK<-plK%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=plK)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)
pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(plK,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,scalecolor=scalecolorCC,                                 scalefill=scalefillCC,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```

## Calcitriol effect on renal function: GFR

Administered calcitriol had no effect on 6, 24, or 48h GFR.

```{r  GFR ,echo=FALSE,message=FALSE, results="show", warning=FALSE}

# plasma potassium --------------------------
ylab<-"GFR"
title<-"GFR_calcil_cila_alone.tiff"
GFR<-M%>%select(x,gfr,x_units,weight_kg,animal)%>%
  mutate(y=gfr, units_x=x_units, weight=weight_kg)
GFR<-GFR%>%
  filter(x%in%sched_labs_x)%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))

#plot

#analysis
#statistical analysis - lmer followed by bh-adjusted pairwise
model<-lmer(y~tx*as.factor(x)+(1|animal),data=GFR)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="sidak")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)

pair_summary<-pair_summary%>%mutate(star=(ifelse(p.value<0.05,
                                                 (ifelse(p.value<0.01, 
                                                         (ifelse(p.value<0.001,"***","**")),
                                                         "*")),"")))

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)


p<-column_scatter_errorbar_plot(GFR,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,scalecolor=scalecolorCC,                                 scalefill=scalefillCC,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                bracket_nudge=0,
                                xlabel="Time (h)",ylabel=ylab)


#write the plot
print(p)

```



## Effect of administered calcitriol on plasma calcitriol

Lastly, we tested (in a subset of animals) whether plasma calcitriol was increased by administered calcitriol. There was wide variation, but no statistically significant effect of calcitriol administration on calcitriol plasma level.

```{r vitamin D assay, echo=FALSE,message=FALSE, results="show", warning=FALSE}
title<-"plasma Calcitriol_calcil_vs_cila.tiff"
ylab<-"Plasma Calcitriol (pg/mL)"

plCal<-M%>%select(x,plCal,plCal_units,weight_kg,animal)%>%
  mutate(y=plCal, units_y=plCal_units, weight=weight_kg)
plCal<-plCal%>%
  mutate(tx=factor(case_when(
    animal%in%cila_only_tx ~ "cila_alone",
    animal%in%cal_tx ~ "calcil",
    animal%in%sham_sx ~ shamname,
    animal%in%veh_tx ~ "veh",
                   )
                   ))%>%
  group_by(tx,x)%>%mutate(mean=mean(y,na.rm=TRUE),sd=sd(y,na.rm=TRUE),sem=sd/n())%>%ungroup()%>%
  filter(!is.na(y))%>%
  filter((tx=="cila_alone")|(tx=="calcil"))%>%
  filter(x%%1==0)%>%
  filter((x>=-1)&(x<=48))



model<-lmer(y~tx*as.factor(x)+(1|animal),data=plCal)
#print(summary(model))     
emm_model <- emmeans(model,~tx*as.factor(x),level=0.95)
#emm_means<-print(emm_model)
pairs_model<-pairs(emm_model,by = "x", adjust="bh")
confint_model<-confint(pairs_model,by = "x")
spairs<-summary(df<-summary(pairs_model))
pair_summary<-summary(pairs_model)
results_flextable(pair_summary)

pair_summary<-pair_summary%>%rowwise()%>%mutate(star=pstar(p.value, write_out_ns=FALSE))%>%ungroup()

my<-max(summary(emm_model)$emmean)
brackets_table<-pairs_to_significance_table(pair_summary,my)

p<-column_scatter_errorbar_plot(plCal,x=factor(x),y=y, groupvar=tx,themevar=plot_theme_wide,scalecolor=scalecolorCC,                                 scalefill=scalefillCC,
                                p_brackets=FALSE,p_bracketsdata=brackets_table,
                                xlabel="Time (h)",ylabel=ylab)

thisplot_left_legend<-c(0.13,0.95)
p<-p+theme(legend.position = left_legend)
print(p)
          

```